Verifying Demonstrations

### 2018-02-28 paper/protocol.tex
Removes \subsubsections, turns into \emphs
Fixes protocol figure, splits between parts

\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
      W\colon & t_s'\gets \TSget \\
      P\colon & cid\gets \Hash[\text{manifesto}], \\
        & pid\gets \ACprf[_{k_P}][cid]
      & \text{\small Join} \\ \midrule && \text{\small Participation} \\[-1.5em]
      P\to W\colon & pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
      W\colon & wid\gets \ACprf[_{k_W}][pid], \\
        & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
      W\to P\colon & (wid, t_s, t_s', l, wsig)
      & \text{\small Participation} \\ \midrule && \text{\small Submission} 
      \\[-1.5em]
      W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
      \text{where} \\
        & \pi_W = \SPK\mleft\{ (k_W) : \mright. \\
        & \qquad wid = \ACprf[_{k_W}][pid], \\
        & \qquad wsig = \ACprf[_{k_W}][wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][k_W]]\mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
      \text{where}\\
        & \pi_P = \SPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO\@.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
      W\colon & t_s'\gets \TSget \\
      P\colon & cid\gets \Hash[\text{manifesto}], \\
        & pid\gets \ACprf[_{k_P}][cid] \\[-1em]
      \noalign{\hfill\small Join}
      \midrule
      \noalign{\hfill\small Participation}
      \\[-3em]
      P\to W\colon & pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
      W\colon & wid\gets \ACprf[_{k_W}][pid], \\
        & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
      W\to P\colon & (wid, t_s, t_s', l, wsig) \\[-1em]
      \noalign{\hfill\small Participation}
      \midrule
      \noalign{\hfill\small Submission}
      \\[-2em]
      W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
      \text{where} \\
        & \pi_W = \SPK\mleft\{ (k_W) : \mright. \\
        & \qquad wid = \ACprf[_{k_W}][pid], \\
        & \qquad wsig = \ACprf[_{k_W}][wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][k_W]]\mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
      \text{where}\\
        & \pi_P = \SPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}
